### 2019-11-28 Mathematical Statistics/ms_ch_04.rmd
mathematical statistics, ch 4
mathematical statistics, ch 4

```{r, echo = T, fig.height=3.5, fig.width=8}
```

Describe the distribution.

@@

```{r, echo = T}
```

@@

Compare the distribution to part (a).

@@

>>>>

```{r, echo = T, fig.height=3.5, fig.width=8}
N <- 10e2
results <- numeric(N)

for(i in 1:N)
{
   samp.a <- sample(A, 3, replace = F)
   samp.b <- sample(B, 3, replace = F)

   results[i] <- max(samp.a) + max(samp.b) 
}

ggplot(data.table(value = results)[, index := .I]) +
   geom_histogram(aes(value, fill = ..count..), bins = 30) +
   labs(title = "Sampling Distribution: max(A) + max(B)")

@@

```{r, echo = T}
prob <- mean(results < 20)
```

Probability: `r prob*100`%

@@

```{r, echo = T, fig.height=3.5, fig.width=8}
results <- numeric(N)

for(i in 1:N)
{
   samp.a <- sample(A, 3, replace = F)
   samp.b <- sample(B, 3, replace = F)

   results[i] <- max(union(samp.a, samp.b))
}

ggplot(data.table(value = results)[, index := .I]) +
   geom_histogram(aes(value, fill = ..count..), bins = 30) +
   labs(title = "Sampling Distribution: max(union(A,B))")
```

@@

```{r, echo = T}
prob <- mean(results < 20)
```

Probability: `r prob*100`%
